### 2018-06-11 FrascatiPlot/Paper/NucleiB2.tex
small changes, next is the big change about the harmonic oscillator potential

\begin{abstract}
(Anti-)(hyper-)nuclei are unique probes of the medium created in proton-proton, proton-Pb, and Pb--Pb collisions at LHC energies. At LHC energies, their production is typically discussed within the framework of coalescence and thermal-statistical production models. While it is often argued that both approaches are not distinguishable, we present a detailed study of both theories which reveals largely different predictions between the two approach for the production of \hethree\ and hyper-tritons. Confronting our results with recent ALICE measurements, the coalescence approach is found to provide a correct description of the data only in small systems such as pp collisions, while it fails for central Pb--Pb collisions. The thermal-statistical model on the other hand is in agreement with results in central Pb--Pb collisions even though such fragile objects should be destroyed in hadronic interactions after the chemical freeze-out of the system. Our findings thus indicate the existence of a novel production mechanism for these objects.
\end{abstract}

@@

\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energy.
Since at LHC energies the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
\begin{equation}
E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right..
\label{eq:BA}
\end{equation}
%
Moreover, the LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}.
In a simple coalescence approach, the coalescence parameter is expected to be independent of \pt~and of the object size with respect to the volume of particle emission (hereafter referred to as ``source volume'' or ``source size'').
In this naive expectation, the number of nuclei produced by coalescence increases with increasing number of nucleons produced in the collision. If the nucleon number increases with the event multiplicity, so does the number of (anti-)nuclei. 
While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, ALICE:nucleipPb2018}, it breaks down in \PbPb~collisions, that exhibit a strong decrease of $B_{A}$ with the centrality of the collision \cite{ALICE:deuteronppPbPb2015}. 
In addition, the elliptic flow of deuteron cannot be explained by simple coalescence \cite{ALICE:deuteronflow2017}.

>>>>

\begin{abstract}
(Anti-)(hyper-)nuclei are unique probes of the medium created in proton-proton, proton-Pb, and Pb--Pb collisions at LHC energies. At LHC energies, their production is typically discussed within the framework of coalescence and thermal-statistical production models. While it is often argued that both approaches are not distinguishable, we present a detailed study of both theories which reveals largely different predictions between the two approach for the production of \hethree\ and hyper-tritons. Confronting our results with recent ALICE measurements, the coalescence approach is found to provide a correct description of the data only in small systems such as pp collisions, while it fails for central Pb--Pb collisions. The thermal-statistical model on the other hand is in agreement with results in central Pb--Pb collisions even though such fragile objects should be destroyed in hadronic interactions after the chemical freeze-out of the system. Our findings thus indicate the existence of a novel production mechanism for these objects and highlight the unique potential of ultra-relativistic heavy-ion collisions as a laboratory to clarify the internal structure of exotic QCD objects.
\end{abstract}

@@

\noindent where $p_{\mathrm{p,n}}$ are the momenta of the proton and neutron and $E_{p,n}$ their energy.
Since at LHC energies the number of produced protons and neutrons at midrapidity is expected to be equal, the equation simplifies to 
\begin{equation}
E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p}}\frac{\mathrm{d}^{3}N_{\mathrm{p}}}{\mathrm{d}p_{\mathrm{p}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\frac{\vec{p}_{A}}{A}} \right..
\label{eq:BA}
\end{equation}
%
Moreover, the LHC is particularly suited for the production of anti-nuclei, since the number of baryons and anti-baryons is essentially equal at midrapidity \cite{Abbas:2013rua}.
In a simple coalescence approach, the coalescence parameter is expected to be independent of \pt~and of the object size with respect to the volume of particle emission (hereafter referred to as ``source volume'' or ``source size'').
In this naive expectation, the number of nuclei produced by coalescence increases with increasing number of nucleons produced in the collision. If the nucleon number increases with the event multiplicity, so does the number of (anti-)nuclei. 
While this picture is found to be approximately valid in pp and \pPb~collisions \cite{ALICE:nucleipp2017, ALICE:nucleipPb2018}, it breaks down in \PbPb~collisions, that exhibit a strong decrease of $B_{A}$ with the centrality of the collision \cite{ALICE:deuteronppPbPb2015}. 
In addition, the elliptic flow of deuterons cannot be explained by simple coalescence \cite{ALICE:deuteronflow2017}.
